An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-09 gas-adsorption/rsc-gas-ads-complete.tex
fix plot, and some edits on the paper

We follow Coudert et al. \cite{coudert2008thermodynamics} in developing a thermodynamic model for a two-phase adsorbent. 
Let $\Delta F=F_{\text{open}}-F_{\text{closed}}$ be the Helmholtz free energy difference per mole of adsorbent between the two phases in the absence of gas.
Suppose the closed phase is more stable ($\implies \Delta F >0$), so that upon a reduction in the pressure of the gas, the material will collapse and expel all residual gas to enhance the deliverable capacity compared to rigid materials that will retain some gas at $\pempty$. 
In addition, assume the open phase hosts a uniform, attractive potential energy field $\V<0$ for gas molecules to adsorb, so that eqn.~\ref{eq:xi_vs_xi0} holds for the open phase of the material.
In terms of $\rho_g(\mu, T)$, then, the grand potential $\Omega$ in our idealized substrate is:
\begin{equation}
    \Omega(T, \mu) = - \int_{-\infty}^\mu \rho_g(\mu-\V)d\mu.
\end{equation}
However, the \emph{osmotic potential} 
% David: introduce units of delta G here.

>>>>

We follow Coudert et al. \cite{coudert2008thermodynamics} in developing a
thermodynamic model for a two-phase adsorbent. Let $\Delta
F=F_{\text{open}}-F_{\text{closed}}$ be the Helmholtz free energy difference per
mole of adsorbent between the two phases in the absence of gas. Suppose the
closed phase is more stable ($\implies \Delta F >0$), so that upon a reduction
in the pressure of the gas, the material will collapse and expel all residual
gas to enhance the deliverable capacity compared to rigid materials that will
retain some gas at $\pempty$. In addition, assume the open phase hosts a
uniform, attractive potential energy field $\V<0$ for gas molecules to adsorb,
so that eqn.~\ref{eq:xi_vs_xi0} holds for the open phase of the material.  This
approximate model of the two-phase material has no upper bound on the
deliverable capacity, since $\V$ and $\Delta F$ can together be increased
without bound.  We can, however, place a bound for a fixed $\Delta F$, since if
the gas is too strongly attracted to the open phase, the material will remain
open at $\pempty$ and our rigid upper bound applies.

The upper bound for the two-phase material is found by identifying the
attractive interaction $\V$ that balances the gas-host attractions in the
idealized-open-substrate at $\pempty$ with the free energy penalty to open.

In
terms of $\rho_g(\mu, T)$, then, the grand potential $\Omega$ in our idealized
substrate is:
\begin{equation}
    \Omega(T, \mu) = - \int_{-\infty}^\mu \rho_g(\mu-\V)d\mu.
\end{equation}
However, the \emph{osmotic potential} governs which phase the material adopts.
The material changes phases when osmotic potentials of the two phases are equal.
% At the pressure at which they switch when the osmotic potentials in the two phases
% are equal.
The upper bound for the two-phase material is found by identifying the largest
possible attraction $|\V|$ consistent with the material transitioning between
$\pempty$ and $\pfull$ to expel all residual gas.
%
This means the material should change phases at pressure $\pempty$, which gives
\begin{align}
    % F_{closed} + 0 &= F_{open} + \Omega(T, \mu) \\
    \frac{\Delta F}{V_{\text{open}}} &= \int_{-\infty}^{\muempty} \rho_g(\mu-\V_{opt})d\mu.
\end{align}
where we follow Coudert \emph{et al.}\cite{coudert2008thermodynamics} and
neglect the $pV$ terms, and $V_{\text{open}}$ is the molar volume of the open
phase.

% David: introduce units of delta G here.
